# Results

```{r}
# Set repository
options(repos = c(CRAN = "https://cloud.r-project.org"))

# Install packages
install.packages(c("dplyr", "readr", "naniar", "ggplot2"))
```


```{r}
# Load libraries
library(dplyr)
library(readr)
library(naniar)
library(ggplot2)
library(forcats)
```

```{r}
merged_data <- readRDS("merged_data.rds")
cleaned_data <- merged_data %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), median(., na.rm = TRUE), .))) %>%
  filter(!is.na(`Churn Category`))
```

```{r}
colnames(cleaned_data)
```


```{r}
ggplot(cleaned_data, aes(x = fct_infreq(`Churn Category`))) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(title = "Distribution of Churn Categories", x = "Churn Category", y = "Count") +
  theme_minimal()
```
From the barplot for Churn Category, we can see that the biggest category is competitor, which is way higher in count than all of the other categories. It suggests that the most reason for customer churn is related to the competition among businesses. We can further verify this by checking the frequency for the specific reasons for customer churn as follows.

```{r}
cleaned_data$`Churn Reason_lumped` <- fct_lump_n(
  cleaned_data$`Churn Reason`, n=12, other_level = 'Other')

ggplot(cleaned_data, aes(x = fct_infreq(`Churn Reason_lumped`))) +
  geom_bar(fill = "steelblue", color = "black") +
  labs(title = "Distribution of Churn Reasons", x = "Churn Reason", y = "Count") +
  theme(axis.text.x = element_text(angle = 65, hjust = 1))
```
Since we have many unique reasons in Churn Reason variable, we used lump to show the most 12 frequent reasons in the graph, and the rest of the reasons fall into reason other. From the graph, we can see that there are 4 competitor related reasons in the most 7 frequent reasons, including better devices, better offer, more data, and higher download speeds. Attitude of support person and provider are also frequent reasons, which is in accordance with the graph for Churn category.


```{r}
# Internet Type vs Churn
ggplot(cleaned_data, aes(x = `Internet Type`, fill = `Churn Category`)) +
  geom_bar(position = "fill") +
  labs(title = "Internet Type vs Churn", x = "Internet Type", y = "Proportion") +
  theme_minimal()

# Contract Type vs Churn
ggplot(cleaned_data, aes(x = `Contract.y`, fill = `Churn Category`)) +
  geom_bar(position = "fill") +
  labs(title = "Contract Type vs Churn", x = "Contract Type", y = "Proportion") +
  theme_minimal()

# Unlimited Data vs Churn
ggplot(cleaned_data, aes(x = `Unlimited Data`, fill = `Churn Category`)) +
  geom_bar(position = "fill") +
  labs(title = "Unlimited Data vs Churn", x = "Unlimited Data", y = "Proportion") +
  theme_minimal()

```

```{r}
ggplot(cleaned_data, aes(x = `Monthly Charges`, fill = `Churn Category`)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ `Internet Type`) +
  labs(
    title = "Monthly Charges vs Churn Category by Internet Type",
    x = "Monthly Charges",
    y = "Density"
  ) +
  theme_minimal()

```

```{r}
# Contract vs Tenure vs Churn Category
ggplot(cleaned_data, aes(x = `Tenure in Months`, fill = `Churn Category`)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ `Contract.y`) +
  labs(
    title = "Tenure in Months vs Churn Category by Contract Type",
    x = "Tenure in Months",
    y = "Density"
  ) +
  theme_minimal()

```

```{r}
ggplot(cleaned_data, aes(x = `Avg Monthly GB Download`, fill = `Churn Category`)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ `Unlimited Data`) +
  labs(
    title = "Avg Monthly GB Download vs Churn Category by Unlimited Data",
    x = "Avg Monthly GB Download",
    y = "Density"
  ) +
  theme_minimal()

```

```{r}
ggplot(cleaned_data, aes(x = `Satisfaction Score`, fill = `Churn Category`)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ `Internet Type`) +
  labs(
    title = "Satisfaction Score vs Churn Category by Internet Type",
    x = "Satisfaction Score",
    y = "Density"
  ) +
  theme_minimal()

```

```{r}
ggplot(cleaned_data, aes(x = `Avg Monthly GB Download`, fill = `Churn Category`)) +
  geom_density(alpha = 0.5) +
  labs(title = "Avg Monthly GB Download vs Churn", x = "Avg Monthly GB Download", y = "Density") +
  theme_minimal()

ggplot(cleaned_data, aes(x = `Monthly Charge`, fill = `Churn Category`)) +
  geom_density(alpha = 0.5) +
  labs(title = "Monthly Charge vs Churn", x = "Monthly Charge", y = "Density") +
  theme_minimal()

ggplot(cleaned_data, aes(x = `Tenure in Months`, fill = `Churn Category`)) +
  geom_density(alpha = 0.5) +
  labs(title = "Tenure in Months vs Churn", x = "Tenure in Months", y = "Density") +
  theme_minimal()

```

```{r}
ggplot(cleaned_data, aes(x = City, fill = `Churn Category`)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(title = "City vs Churn", x = "City", y = "Proportion") +
  theme_minimal()

ggplot(cleaned_data, aes(x = State, fill = `Churn Category`)) +
  geom_bar(position = "fill") +
  labs(title = "State vs Churn", x = "State", y = "Proportion") +
  theme_minimal()

```

